On the minimum leaf conductance: its role in models of plant water use, and ecological and environmental controls

### 2018-01-11 manuscript.Rmd
moved table 2 to suppinfo; suppinfo with references and two plots

\ 
We quantitatively compared each of the different 'minimum' conductance (Table 1) values by synthesizing existing data. To estimate g~0~ (Eq. 1) from regression, we used the @lin2015 database to fit the model of @medlyn2011 using non-linear regression, and data presented by @miner2017 on the linear regression of the @ballberry1987 model. Measurements of conductance of isolated, non-stomatal cuticles (g~cut~) were taken from the compilations by @kerstiens1996 and @schuster2017.  Data on minimum conductance (g~min~) from MLD was compiled from 44+ original papers (see SuppInfo 2 for a list of papers). For the compilation, we returned to all original papers mentioned in the review by @kerstiens1996, and added many newer sources. All conductance values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). Although it is quite clear that night-time conductance (g~dark~) is much larger than a true 'minimum' conductance (discussed further in Section VI), it is frequently used as an independent measurement of g~0~ [@lombardozzi2017], and thus a comparison of magnitudes is useful. A compilation of night-time conductance (g~dark~) values was taken from @lombardozzi2017, who compiled cuvette (and sometimes sap flow-based) measurements of ca. 150 species during night-time. Actual minimum daytime values were estimated from the @lin2015 database, by taking those data where A~n~ < 2 $mu$ mol m^-2^ s^-1^, and calculating the minimum g~s~ for each of the XXX studies included in that dataset. This estimate was added as a reference as it represents an actual minimum values measured, rather than a fitted/extrapolated g~0~ term.

@@

\
From the literature we found a general acclimatory response of g~min~ to drought stress, nearly always leading to a significant  decrease in g~min~ (see Table 2 for a summary of the literature), with just one exception. In each of the studies summarized, plants were grown in well-watered or droughted conditions, and in one case a difference in g~min~ was demonstrated after just four days of drought exposure [@bengtson1978]. We also demonstrate drought acclimation via a case study on 11 *Hakea* species grown in two watering treatments (Fig. 7).

@@

```{r, echo=FALSE}
dat <- read.csv("data/drought_gmin_table.csv", stringsAsFactors = FALSE)

knitr::kable(dat, 
             caption="**Table 2.** Summary of studies demonstrating a decrease in g~min~ after an acclimation period to low soil water availability",
             col.names= c("Study","Species","Experiment","Reduction in g~min~"))
```

@@

## 5. Other factors

Also discussed above in Section~(cuticular conductance), the cuticle is constantly exposed to physical (wind, rain) and biotic (insects, fungi) agents which damage the cuticle over time.

@jordan2007 large increase gmin in the herb Agastachys odorata with leaf age. (*Several studies in database that have leaf age effects; summarize?*).

@anfodillo2002 gmin high altitude. Four-fold increase gmin from February (winter) to August in Picea abies, probably due to incomplete stomatal closure not changes in cuticle properties. Cite common finding that gmin increases with altitude [e.g. @delucia1984; @herrick1991].

@fanourakis2013 gmin (MLD) much higher in high RH grown plants, at any value of leaf water content (Table 1). This may suggest that gmin is useful for the plant, and is reduced actively in response to water loss (Hypothesis 2). (*could go to temperature section, as T and RH are correlated in field conditions*).

>>>>

\ 
We quantitatively compared each of the different 'minimum' conductance (Table 1) values by synthesizing existing data. To estimate g~0~ (Eq. 1) from regression, we used the @lin2015 database to fit the model of @medlyn2011 using non-linear regression, and data presented by @miner2017 on the linear regression of the @ballberry1987 model. Measurements of conductance of isolated, non-stomatal cuticles (g~cut~) were taken from the compilations by @kerstiens1996 and @schuster2017.  Data on minimum conductance (g~min~) from MLD was compiled from 40 original papers (see SuppInfo 2 for references). For the compilation, we returned to all original papers mentioned in the review by @kerstiens1996, and added many newer sources. All conductance values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). Although it is quite clear that night-time conductance (g~dark~) is much larger than a true 'minimum' conductance (discussed further in Section VI), it is frequently used as an independent measurement of g~0~ [@lombardozzi2017], and thus a comparison of magnitudes is useful. A compilation of night-time conductance (g~dark~) values was taken from @lombardozzi2017, who compiled cuvette (and sometimes sap flow-based) measurements of ca. 150 species during night-time. Actual minimum daytime values were estimated from the @lin2015 database, by taking those data where A~n~ < 2 $mu$ mol m^-2^ s^-1^, and calculating the minimum g~s~ for each of the XXX studies included in that dataset. This estimate was added as a reference as it represents an actual minimum values measured, rather than a fitted/extrapolated g~0~ term.

@@

\
From the literature we found a general acclimatory response of g~min~ to drought stress, nearly always leading to a significant  decrease in g~min~ (see Table S2 for a quantitative summary of the literature), with just one exception. The magnitude of the decrease of g~min~ with acclimation to drought stress varied from -4 to -70%; no attempt at a meta analysis was made since no drought is created equal. In each of the studies summarized, plants were grown in well-watered or droughted conditions, and in one case a difference in g~min~ was demonstrated after just four days of drought exposure [@bengtson1978]. We also demonstrate drought acclimation via a case study on 11 *Hakea* species grown in two watering treatments (Fig. 7).

@@

\
atmospheric drought
@fanourakis2013 gmin (MLD) much higher in high RH grown plants, at any value of leaf water content. This may suggest that gmin is useful for the plant, and is reduced actively in response to water loss.

@@

## 5. Increased minimum conductance with leaf age

@jordan2007 large increase gmin in the herb Agastachys odorata with leaf age. See SuppInfo 3 for a summary of six studies on leaf age effects. All but one species show an increase in g~min~ with leaf age. Also discussed above in Section~(cuticular conductance), the cuticle is constantly exposed to physical (wind, rain) and biotic (insects, fungi) agents which damage the cuticle over time.

- do any of those papers say why? summarize

@anfodillo2002 gmin high altitude. Four-fold increase gmin from February (winter) to August in Picea abies, probably due to incomplete stomatal closure not changes in cuticle properties. Cite common finding that gmin increases with altitude [e.g. @delucia1984; @herrick1991]. @fernandez2017 summarized the literature on this topic and argue that the short growing seasons at high altitude cause 'unripe' cuticles.
